---
title: ''
output: pdf_document
---

\subsubsection{Simulations with Varying Levels of List Dependency }
\label{Sec:simslistdepend}

The objective of this subsection is to evaluate the BLRCR and other models under varying coefficients that induce different levels of list dependency. All of this list dependency is really just heterogeneity in the capture probabilities that can be fully explained by the covariates. The models that do not use covariates (Log Linear, LCMCR, and Independent) will not or will struggle to detect the heterogeneity leading to biased results.  On the other hand, the BLRCR and cMLCR will perform well as they incorporate the covariates into their modelling.

We simulate data in accordance with \autoref{eqn:logitdatacreation} using two covariates ($H$=2) and four lists ($J=4$).  The covariates are drawn from two independent standard normal distributions.  Three sets of $\beta$ coefficients are chosen that create "negative", "moderate", and "positive" dependency between the lists and are described in \autoref{table:1}. To clarify, all of the lists regardless of the coefficients are conditionally independent given the covariates.  We simulate an additional dataset with all of the slope coefficients set to 0, thereby creating lists with independent capture probabilities.

\singlespacing
\begin{table}[H]
\centering
\begin{tabular}{||c c c c||} 
 \hline
 \multicolumn{4}{||c||}{"Negative"}\\
 \hline
 List ($j$) & $\beta_{0j}$ & $\beta_{1j}$ & $\beta_{2j}$   \\ [0.5ex] 
 \hline\hline
 1 & -2 &  -1  & 1 \\ 
 2 & -2 & 1  &  -1 \\
 3 & -2 & 1  &  1 \\
 4 & -2 &  -1  &  -1 \\
 \hline
\end{tabular}
\begin{tabular}{||c c c c||} 
\hline
 \multicolumn{4}{||c||}{"Moderate"}\\
 \hline
 List ($j$) & $\beta_{0j}$ & $\beta_{1j}$ & $\beta_{2j}$   \\ [0.5ex] 
 \hline\hline
 1 & -2 &  -1  & 1 \\ 
 2 & -2 & 1  &  -1 \\
 3 & -2 & -1  &  1 \\
 4 & -2 &  1  &  -1 \\
 \hline
\end{tabular}
\begin{tabular}{||c c c c||} 
 \hline
 \multicolumn{4}{||c||}{"Positive"}\\
 \hline
 List ($j$) & $\beta_{0j}$ & $\beta_{1j}$ & $\beta_{2j}$   \\ [0.5ex] 
 \hline\hline
 1 & -2 &  -1  & 1 \\ 
 2 & -2 & -1  &  1 \\
 3 & -2 & -1  &  1 \\
 4 & -2 &  -1  &  1 \\
 \hline
\end{tabular}
\caption{Coefficients for Simulated Data}
\label{table:1}
\end{table}
\doublespacing

```{r}
##################################
### Different Coefficients #######
##################################

##########
#Moderate#
##########
#Set N and BETA
myN=2000
myBeta="moderate"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates=="twonormalcovs"

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```

\singlespacing
\begin{table}[H]
\centering
\begin{tabular}{||r l r r r r||} 
 \hline
$\boldsymbol{\beta}$ & Method & N$\%$ &MSE & CI Width & CI $\%$   \\ [0.5ex] 
 \hline\hline
 "Moderate"    & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               &  BLRCR($K=20$, $H_\omega=1$)   & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\                
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 
               
```{r}
##########
#Negative#
##########
#Set N and BETA
myN=2000
myBeta="negative"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates=="twonormalcovs"

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```
                                  
 \hline
"Negative"    & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
                              & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\                
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\
```{r}
##########
#Positive#
##########
#Set N and BETA
myN=2000
myBeta="positive"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates=="twonormalcovs"

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```
 \hline
 "Positive"    & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\                
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 
```{r}
#############
#Independent#
#############
#Set N and BETA
myN=2000
myBeta="independent"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates=="twonormalcovs"

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```
 \hline
 "Independent" & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\                
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 
 \hline
\end{tabular}
\caption{Results of 100 capture-recapture simulations per coefficient set using $N=2000$ with "Moderate", "Negative", "Positive", and "Independent" list dependency with two standard normal covariates. }
\label{table:diffcoefs}
\end{table}
\doublespacing

\autoref{table:diffcoefs} shows the results from 100 simulated datasets for each set of coefficients, $\beta$. While all of the models performed well when the slope coefficients were set to 0, i.e. "Independent", the methods using covariates (BLRCR and cMLRCR) showed substantially less bias than the other methods when coefficients impacted the capture probability, i.e. "Moderate", "Negative", and "Positive". This illustrates the importance of including covariates in the estimation process.  Nevertheless, the two methods that account for unknown heterogeneity, log linear and LCMCR, still performed remarkably well when the list dependency was set to be "negative."  Unfortunately, "positively" induced list dependency led to a substantial decline in performance.
