---
title: ''
output: pdf_document
---

\subsection{Simulations with Unobserved Heterogeneity}
\label{Sec:simsunobservedheterogeneity}

The final set of simulations is to demonstrate the importance of accounting for both the observed and unobserved heterogeneity. While the cMLCR model has performed well in the prior sections, it has no method of detecting unobservable heterogeneity and hence produces biased estimation. Interestingly, a model like the LCMCR, which is designed to account for unobservable heterogeneity, performs much better, but still struggles as considerable information can be gained by including the covariates. The BLRCR model when extended to include latent intercepts ($H_\omega>1$) can utilize the covariates to detect the observable heterogeneity, but also accounts for the additional unobservable heterogeneity.  As a result, it is the only model that performs well in this subsection.

Data is simulated for three lists (J=3) with one standard normally distributed observed covariate (H=1) and one unobserved covariate indicating membership to a latent group with probability 0.35.  The coefficients used to simulate the data can be found in \autoref{table:heterocoefs}.  Using these coefficients induces positive dependency between lists 1 and 2, but negative dependency between list 3 and the other two lists.  If class membership were known, the list probabilities would still be conditionally independent; however, since these covariates are unobserved, the list probabilities are no longer conditionally independent given the observed data.

\singlespacing
\begin{table}[H]
\centering
\begin{tabular}{||c c c c||} 
 \hline
 List ($j$) & $\beta_{0j}$ & $\beta_{1j}$ & $\beta_{\omega j}$   \\ [0.5ex] 
 \hline\hline
 1 & -2.5 &  -1.5  & 3.0 \\ 
 2 & -2.5 & -1.5  &  3.0 \\
 3 & 0.5 & -1.5  &  -3.0 \\
 \hline
\end{tabular}
\caption{Coefficients for Heterogeneity Simulated Data}
\label{table:heterocoefs}
\end{table}
\doublespacing


\autoref{table:heterodist} shows the results of 100 simulations on four different population sizes.  It becomes obvious that not accounting for unobserved heterogeneity results in biased estimates for both the BLRCR and cMLCR models.  Recall, the truth with these simulations is there exists two latent classes.  Notice the BLRCR model with the number of hidden classes set at $H_\omega=2$ performs the best in terms of both accuracy and precision.  In a real setting, the number of hidden classes would almost certainly be unknown so we set a sufficiently large value $H_\omega=20$.  While the model doesn't perform quite as well as the aforementioned setting, it dramatically outperforms the methods that do not take unobserved heterogeneity into account.

For situations where observed and unobserved heterogeneity exist, we need a method that accounts for both. It should be noted that the LCMCR model, a methodology that doesn't use covariates, is outperforming the methods that do but assume conditional independence. The LCMCR model is designed to account for unobserved heterogeneity, and since the unobserved heterogeneity plays a substantial role in the capture probability for these simulations, it performs reasonably well. Of course, as we saw in the previous subsections' simulations, the LCMCR does not perform as well as the other methods when most of the heterogeneity can be explained by the covariates.

To further explore the effects of hidden heterogeneity and its detectability, we ran 100 simulations with different coefficients and group percentages.  Using the same coefficients in \autoref{table:heterocoefs}, but adjusting the absolute value of the coefficients, $\beta_{\omega_j}$, we created scenarious that depict different strength levels of heterogeneity.  Trivially, if the coefficient is 0, there is no unobserved heterogeneity in the capture probabilities.  In this situation the algorithm is simply detecting noise that it is mistaking for heterogeneity.  On the other hand, when the absolute value of the $\beta_{\omega j}$ coefficients are set to 5, there is very strong heterogeneity in the capture probabilities for the two groups.  The top plot in \autoref{fig:heterogeneitydiff} shows the mean square error (MSE) of the 100 simulations' posterior median of $N$. A close examination of the plot reveals an overall decrease in the MSE as the heterogeneity strengthens.  This is not surprising as the model is attempting to account for heterogeneity, but if it cannot detect the heterogeneity, it will induce bias.  When the heterogeneity is stronger, the model is more likely to detect this heterogeneity and account for it properly.  

\singlespacing
\begin{table}[H]
\centering
\begin{tabular}{||r l r r r r||} 
 \hline
N & Method & N$\%$ &MSE & CI Width & CI $\%$   \\ [0.5ex] 
 \hline\hline

```{r}
#########################################################
####### Heterogeneity Distributions #####################
#########################################################
#Set N and BETA
myN=1000
myBeta="heterogeneity"
mycovariates="onenormwithheterocovs"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates==mycovariates

#test=simdat[myindex,]
#mean(as.numeric(test$cBLRCR))

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
HSPBLRCR2Nhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
HSPBLRC2RMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR2.50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
HSPBLRC2width = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
HSPBLRC2CI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```

 1000          & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=2$)    & `r op(HSPBLRCR2Nhat,3)`     & `r op(HSPBLRC2RMSE,1)`     & `r op(HSPBLRC2width,3)`     & `r op(HSPBLRC2CI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\ 
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 

 \hline
 
```{r}
#########################################################
####### Heterogeneity Distributions #####################
#########################################################
#Set N and BETA
myN=2000
myBeta="heterogeneity"
mycovariates="onenormwithheterocovs"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates==mycovariates

#test=simdat[myindex,]
#mean(as.numeric(test$cBLRCR))

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
HSPBLRCR2Nhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
HSPBLRC2RMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR2.50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
HSPBLRC2width = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
HSPBLRC2CI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```

 2000          & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\
               & BLRCR($K=20$, $H_\omega=2$)    & `r op(HSPBLRCR2Nhat,3)`     & `r op(HSPBLRC2RMSE,1)`     & `r op(HSPBLRC2width,3)`     & `r op(HSPBLRC2CI,1)` \\
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\ 
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 

 \hline
 
```{r}
#########################################################
####### Heterogeneity Distributions #####################
#########################################################
#Set N and BETA
myN=5000
myBeta="heterogeneity"
mycovariates="onenormwithheterocovs"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates==mycovariates

#test=simdat[myindex,]
#mean(as.numeric(test$cBLRCR))

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
HSPBLRCR2Nhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
HSPBLRC2RMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR2.50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
HSPBLRC2width = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
HSPBLRC2CI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```

 5000          & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=2$)    & `r op(HSPBLRCR2Nhat,3)`     & `r op(HSPBLRC2RMSE,1)`     & `r op(HSPBLRC2width,3)`     & `r op(HSPBLRC2CI,1)` \\
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\ 
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 

 \hline
 
```{r}
#########################################################
####### Heterogeneity Distributions #####################
#########################################################
#Set N and BETA
myN=10000
myBeta="heterogeneity"
mycovariates="onenormwithheterocovs"
myindex <- simdat$N==myN & simdat$BETA==myBeta & simdat$covariates==mycovariates

#test=simdat[myindex,]
#mean(as.numeric(test$cBLRCR))

#Compute Percentage of N
HSPBLRCRNhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR50))/myN
HSPBLRCR2Nhat = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.50))/myN
SPBLRCRNhat = mean(as.numeric(simdat[myindex,]$SPBLRCR50))/myN
normBLRCRNhat = mean(as.numeric(simdat[myindex,]$normBLRCR50))/myN
cMLCRNhat = mean(as.numeric(simdat[myindex,]$cMLCR))/myN
cBLRCRNhat = mean(as.numeric(simdat[myindex,]$cBLRCR))/myN
LCMCRNhat = mean(as.numeric(simdat[myindex,]$LCMCR50))/myN
loglinNhat = mean(as.numeric(simdat[myindex,]$loglin50))/myN
IndependentNhat = mean(as.numeric(simdat[myindex,]$Independent50))/myN

#Check RMSE
HSPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR50),myN)
HSPBLRC2RMSE = RMSE(as.numeric(simdat[myindex,]$HSPBLRCR2.50),myN)
SPBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$SPBLRCR50),myN)
normBLRCRMSE = RMSE(as.numeric(simdat[myindex,]$normBLRCR50),myN)
cMLCRRMSE = RMSE(as.numeric(simdat[myindex,]$cMLCR),myN)
cBLRCRRMSE = RMSE(as.numeric(simdat[myindex,]$cBLRCR),myN)
LCMCRRMSE = RMSE(as.numeric(simdat[myindex,]$LCMCR50),myN)
loglinRMSE = RMSE(as.numeric(simdat[myindex,]$loglin50),myN)
IndependentRMSE = RMSE(as.numeric(simdat[myindex,]$Independent50),myN)

#Average width of interval
cMLCRwidth = mean(as.numeric(simdat[myindex,]$cMLCR97.5)-as.numeric(simdat[myindex,]$cMLCR2.5))/myN
HSPBLRCwidth = mean(as.numeric(simdat[myindex,]$HSPBLRCR97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.5))/myN
HSPBLRC2width = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)-as.numeric(simdat[myindex,]$HSPBLRCR2.2.5))/myN
SPBLRCwidth = mean(as.numeric(simdat[myindex,]$SPBLRCR97.5)-as.numeric(simdat[myindex,]$SPBLRCR2.5))/myN
normBLRCwidth = mean(as.numeric(simdat[myindex,]$normBLRCR97.5)-as.numeric(simdat[myindex,]$normBLRCR2.5))/myN
LCMCRwidth = mean(as.numeric(simdat[myindex,]$LCMCR97.5)-as.numeric(simdat[myindex,]$LCMCR2.5))/myN
loglinwidth = mean(as.numeric(simdat[myindex,]$loglin97.5)-as.numeric(simdat[myindex,]$loglin2.5))/myN
Independentwidth = mean(as.numeric(simdat[myindex,]$Independent97.5)-as.numeric(simdat[myindex,]$Independent2.5))/myN

#Check Percentage in Interval
cMLRCCI = mean(as.numeric(simdat[myindex,]$cMLCR2.5)<myN&as.numeric(simdat[myindex,]$cMLCR97.5)>myN)*100
HSPBLRCCI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR97.5)>myN)*100
HSPBLRC2CI = mean(as.numeric(simdat[myindex,]$HSPBLRCR2.2.5)<myN&as.numeric(simdat[myindex,]$HSPBLRCR2.97.5)>myN)*100
SPBLRCCI = mean(as.numeric(simdat[myindex,]$SPBLRCR2.5)<myN&as.numeric(simdat[myindex,]$SPBLRCR97.5)>myN)*100
normBLRCCI = mean(as.numeric(simdat[myindex,]$normBLRCR2.5)<myN&as.numeric(simdat[myindex,]$normBLRCR97.5)>myN)*100
LCMCRCI = mean(as.numeric(simdat[myindex,]$LCMCR2.5)<myN&as.numeric(simdat[myindex,]$LCMCR97.5)>myN)*100
loglinCI = mean(as.numeric(simdat[myindex,]$loglin2.5)<myN&as.numeric(simdat[myindex,]$loglin97.5)>myN)*100
IndependentCI = mean(as.numeric(simdat[myindex,]$Independent2.5)<myN&as.numeric(simdat[myindex,]$Independent97.5)>myN)*100
```

 10000          & BLRCR($K=1$, $H_\omega=1$)  & `r op(normBLRCRNhat,3)`   & `r op(normBLRCRMSE,1)`   & `r op(normBLRCwidth,3)`   & `r op(normBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=1$)    & `r op(SPBLRCRNhat,3)`     & `r op(SPBLRCRMSE,1)`     & `r op(SPBLRCwidth,3)`     & `r op(SPBLRCCI,1)` \\ 
               & BLRCR($K=20$, $H_\omega=2$)    & `r op(HSPBLRCR2Nhat,3)`     & `r op(HSPBLRC2RMSE,1)`     & `r op(HSPBLRC2width,3)`     & `r op(HSPBLRC2CI,1)` \\
               & BLRCR($K=20$, $H_\omega=20$)    & `r op(HSPBLRCRNhat,3)`     & `r op(HSPBLRCRMSE,1)`     & `r op(HSPBLRCwidth,3)`     & `r op(HSPBLRCCI,1)` \\ 
               & cMLCR       & `r op(cMLCRNhat,3)`       & `r op(cMLCRRMSE,1)`      & `r op(cMLCRwidth,3)`      & `r op(cMLRCCI,1)` \\
               & Log Linear (BIC)  & `r op(loglinNhat,3)`      & `r op(loglinRMSE,1)`     & `r op(loglinwidth,3)`     & `r op(loglinCI,1)` \\ 
               & LCMCR       & `r op(LCMCRNhat,3)`       & `r op(LCMCRRMSE,1)`      & `r op(LCMCRwidth,3)`      & `r op(LCMCRCI,1)` \\ 
               & Independent & `r op(IndependentNhat,3)` & `r op(IndependentRMSE,1)`& `r op(Independentwidth,3)`& `r op(IndependentCI,1)` \\ 

 \hline
\end{tabular}
\caption{Results of 100 capture-recapture simulations per algorithm using a standard normal distribution distribution for the known covariate and 0.35 probability of belonging to the latent class.}
\label{table:heterodist}
\end{table}
\doublespacing

```{r heterogeneitydiff, fig.align='center',fig.width=9,fig.height=7,fig.margin=TRUE,fig.cap="\\label{fig:strengthheterogeneitydiff}Effect of Strength of Heterogeneity on the Mean Square Error"}
diffleveldataset<-readRDS("simdata/heterogeneitylevelsdata.RDS")

#Edit the data to get MSE for group identification and N
diffleveldataset$sqdiff = (1-diffleveldataset$N50/5000)^2
diffleveldatasetLONG= cbind(rbind(diffleveldataset[,1:5],diffleveldataset[,1:5]),
                            "AME"=c(diffleveldataset[,9],diffleveldataset[,10]),
                            "param"=c(rep("Group Identity",1800),rep("Estimated N",1800)))

#diffleveldataset$intlength = (diffleveldataset$N97.5-diffleveldataset$N2.5)/5000
#aggregate(cbind(sqdiff,intlength)~beta+percgroup,diffleveldataset,mean)

aggdataframe = cbind(
  aggregate(AME~beta+percgroup+param,diffleveldatasetLONG,mean),
  "lower"=aggregate(AME~beta+percgroup+param,diffleveldatasetLONG,function(x){quantile(x,c(0.025),names=FALSE)})[,4],
  "upper"=aggregate(AME~beta+percgroup+param,diffleveldatasetLONG,function(x){quantile(x,c(0.975),names=FALSE)})[,4])

#do this to truncate the upper limits of the N mse (remove if not desired)
#aggdataframe$upper[which(aggdataframe$upper>.0075&aggdataframe$param=="Estimated N")] = .0075

aggdataframe$beta = as.factor(aggdataframe$beta)
aggdataframe$percgroup = as.factor(aggdataframe$percgroup)
pd=position_dodge(0.2)
par(mfrow=c(1,2))
ggplot(aggdataframe, aes(x=beta, y=AME, group=percgroup,color=percgroup)) + 
  facet_grid(param~.,scales="free") +
  geom_point(position=pd, size=3) +
  geom_line(position=pd, size=1) +
  geom_pointrange(aes(ymin=lower, ymax=upper), size=1,position=pd) +
  xlab("Strength of Heterogeneity") +
  ylab("Mean Square Error") +
  scale_colour_hue(name="Percentage in Group 1",    
                   breaks=c("0.1", "0.3", "0.5"),
                   labels=c("0.1", "0.3", "0.5"),
                   l=30) +  
  theme_classic() +
  theme(legend.justification=c(1,0),
        legend.position=c(.95,.75))      
```

The bottom plot in \autoref{fig:heterogeneitydiff} shows the MSE of the average posterior group identifier for the observed data.  In other words, if the first observation actually belongs to the hidden group, $\omega_1$=1, then we find the average number of times the algorithm placed the observation in the first group, $\bar{\omega}_1$.  In the binary case, $H_\omega=2$, the MSE can be computed as

\begin{equation}
MSE = \frac{1}{n}\sum_{i=1}^n (\bar{\omega}_{i} - \omega_i)^2.
\end{equation}

As the heterogeneity strengthens, the detectability of the unobserved groupings increases and the MSE drops considerably.  In the case where the absolute value of $\beta_{\omega j}$ is set to 5, in many of the simulations between 90 and 95$\%$ of the observations are detected correctly in over 90$\%$ of posterior samples.

Unobserved heterogeneity creates a trade off.  On one hand, if the unobserved heterogeneity is weak, there will be relatively little bias in $N$; however, the ability to detect this heterogeneity decreases as well.  On the other hand, When the unobserved heterogeneity is strong, the bias in $N$ will be relatively larger, but the ability to detect and properly account for this heterogeneity increases. 

